---
title: "p8131_stl2137_hw7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(tidyverse)
```

```{r}
data <- read_csv("/Users/SabrinaLin/Documents/Spring_20_Biostat_Methods_2/Data/HW7-politeness_data.csv")
```

### Question 1
1. Exploratory analysis: provide boxplots to show the relation between gen- der/attitude and pitch (ignoring different scenarios).

```{r}
summary(data)
boxplot(frequency ~ attitude*gender, col=c("white","lightgray"),data= data)
```

### Question 2

2. Fit a mixed effects model with random intercepts for different subjects (gender and attitude being the fixed effects). What is the covariance matrix for a subject Yi? What is the covariance matrix for the REML estimates of fixed effects (hint: 3*3 matrix for intercept, gender and at- titude)? What are the BLUPs for subject-specific intercepts? What are the residuals?
```{r}
m1 <- lmer(frequency ~ gender + attitude + (1|subject), REML = T, data = data)
summary(m1)
round(ranef(m1)$subject,2)
residuals(m1)
```

### Question 3

```{r}
m2 <- lmer(frequency ~ gender + attitude + gender*attitude+ (1|subject), REML = T, data = data)
summary(m2)
ranef(m2)
TS1 <- deviance(m1) - deviance(m2)
p1 <- 1-pchisq(TS1, 1)
anova(m2, m1)
```

### Question 4

```{r}
m3 <- lmer(frequency ~ gender + attitude + (1+attitude|subject), data = data)
summary(m3)
ranef(m3)
```

